Instructions for \confname{} Proceedings

### 2019-05-09 papers/EMNLP2019/analysis.tex
annotation for crossclassified finished
finalized annotation; intial analysis in the explore notebook

\sz{discuss...}

>>>>

Interesting name pairs:

\begin{itemize}
\item storefront - store: strictly speaking it's part-whole, but how can one distinguish between the two? 
\item field - grass: same (reverse); how to distinguish?
\item dog - pet (different conceptualizations; classified as ``overlapping''
\item airplane - flight, plane - flight (classified as ``adjacent'' although it's an event relation...)
\end{itemize}
